---
title: "PSTAT 5LS Winter 2024"
author: "Your Name Here"
date: "Week of January 22, 2024"
output: pdf_document 
---

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Code

You can follow along with the TA's tutorial by running the chunks below. 

```{r loadPenguins, error = T}
# Run this code chunk to load the penguins data set into the environment
penguins <- read.csv("penguins.csv", stringsAsFactors = TRUE)
```

```{r tryIt1, error = T}
# Run this code chunk to peek at the penguins data set
head(penguins)
```

```{r tryIt2, error = T}
# Run this code chunk to examine the structure of the penguins data set
str(penguins)
```

```{r tryIt3, error = T}
# Run this code chunk to make a table of the species variable in the penguins data
table(penguins$species)
```

```{r tryIt4, error = T}
# Run this code chunk to make a two-way frequency table of the variables species and island in the penguins data
table(penguins$species, penguins$island)
```

```{r tryIt5, error = T}
# Run this code chunk to make a bar chart of the species variable in the penguins data
barplot(table(penguins$species),
     xlab = "Species",
     ylab = "Frequency",
     main = "Bar Chart of Number of Penguins of Each Species 
            Observed",
     col = c("darkorange1", "mediumorchid2", "darkcyan"))
```

```{r tryIt6, error = T}
# Run this code chunk to get help with the barplot function
?barplot
```

```{r tryIt7, error = T}
# Run this code chunk to view the summary of the flipper_length_mm variable in the penguins data
summary(penguins$flipper_length_mm)
```

```{r tryIt8, error = T}
# Run this code chunk to view the summary and the standard deviation of the flipper_length_mm variable in the penguins data
summary(penguins$flipper_length_mm)
sd(penguins$flipper_length_mm)
```

```{r tryIt9, error = T}
# Run this code chunk to get all of the specific number summary values
min(penguins$flipper_length_mm)
mean(penguins$flipper_length_mm)
median(penguins$flipper_length_mm)
max(penguins$flipper_length_mm)
sd(penguins$flipper_length_mm)
IQR(penguins$flipper_length_mm)
# Note that IQR is in all capital letters. Anything else (e.g., `iqr(penguins$flipper_length_mm)`) would give you an error
```

```{r tryIt10, error = T}
# Run this code chunk to make a histogram of the variable flipper_length_mm in the penguins data. When you make your own histograms, be sure to add the `main` and `xlab` labels for better readability 
hist(penguins$flipper_length_mm,
     main = "Histogram of Penguin Flipper Length",
     xlab = "Flipper Length (mm)",
     col = "lightblue")
```

```{r tryIt11, error = T}
# Run this code chunk to make a boxplot of the variable flipper_length_mm in the penguins data. Don't forget a title using `main` and a y-axis label using `ylab`.
boxplot(penguins$flipper_length_mm,
        main = "Boxplot of Penguin Flipper Length",
        ylab = "Flipper Length (mm)",
        col = "lightblue")
```

```{r tryIt12, error = T}
# Run this code chunk to make a side-by-side boxplot of penguins body mass by the categorical variable `species`
boxplot(penguins$body_mass_g ~ penguins$species,
        main = "Boxplots of Penguin Body Mass by Species",
        ylab = "Body mass (g)",
        xlab = "Species",
        col = c("darkorange1", "mediumorchid2", "darkcyan"))
```

```{r tryIt13, error = T}
# Run this code chunk to make a side-by-side boxplot of penguins flipper length by the categorical variable `island`
boxplot(penguins$flipper_length_mm ~ penguins$island,
        main = "Boxplots of Penguin Flipper Length by Island",
        ylab = "Flipper Length (mm)",
        xlab = "Island",
        col = c("slateblue2", "dodgerblue2", "mediumaquamarine"))
```

# Code Cheat Sheet

## `$`
- tells R that we are looking for a variable in a particular data frame
- `data_set_name$data_set_variable`

## `table(data_set_name$data_set_variable)`
- creates a table of the frequencies of one categorical variable

## `table(data_set_name$data_set_variable, data_set_name$data_set_variable)`
- creates a two way table of the frequencies of two categorical variables

## `barplot(table(data_set_name$data_set_variable))`
- creates a barplot of a categorical variable

## `summary(data_set_name$data_set_variable)`
- creates the five number summary of a numeric variable

## `hist(data_set_name$data_set_variable)`
- creates a histogram of a numeric variable

## `boxplot(data_set_name$data_set_variable)`
- creates a boxplot of a numeric variable

## `boxplot(data_set_name$numeric_variable ~ data_set_name$categorical_variable)`
- creates side-by-side boxplots of a numeric variable grouped by a categorical variable

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes

