---
title: "PSTAT 5LS Lab 6 Report"
author: "YOUR NAME GOES HERE - KEEP THE QUOTES"
date: "TODAY'S DATE GOES HERE - KEEP THE QUOTES"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats250sbi)
```

# Introduction

The U.S. Department of Transportation's (DOT) Bureau of Transportation Statistics tracks the on-time performance of domestic flights operated by large air carriers. Summary information on the number of on-time, delayed, canceled, and diverted flights is published in DOT's monthly Air Travel Consumer Report and in this dataset of 2015 flight delays and cancellations. We will be working with a cleaned up version of [this data set published by Kaggle](https://www.kaggle.com/usdot/flight-delays?select=flights.csv). 

`delayed_flights.csv` reflects a random sample of only flights leaving from Detroit Metro Airport (DTW) from two airlines: American Airlines (`AA`) and Delta Airlines (`DL`). The airline info can be found in the `AIRLINE` variable. Then, the variable `AIRLINE_DELAY` was cleaned to reflect only actual delay times in minutes (i.e. non-zero, non-negative values for the variable).

## Research Question
Is there evidence to support that there is a difference in the average delay time in minutes (`AIRLINE_DELAY`) for American Airlines flights and Delta Airlines flights (`AIRLINE`) leaving Detroit Metro Airport? Your Lab 7 Report will answer this question.

The parameter of interest is $\mu_1 - \mu_2$ which represents the difference in the average flight delay time for American Airlines and the average flight delay for Delta Airlines, for flights that departed from Detroit Metro Airport.

## Question 1:
What hypotheses do you need to test to determine if there is a difference in the average delay time in minutes (`AIRLINE_DELAY`) for American Airlines flights and Delta Airlines flights (`AIRLINE`) leaving Detroit Metro Airport?

$H_0$: *write your null hypothesis here in symbols (no need to define the symbols again)*

$H_A$: *write your alternative hypothesis here in symbols (no need to define the symbols again)*

## Question 2:
We need to check the conditions for inference before proceeding. 

For one of the conditions, you need to examine the data. First, you need to read in the data. 

```{r chunk1, error = T}
# Run this code chunk to read in the data
delays <- read.csv("delayed_flights.csv", stringsAsFactors = TRUE)
```

Then create histograms for the two samples:

```{r chunk2, error = T}
# Run this code chunk to create a histogram for the flight delays for American Airlines
hist(delays$AIRLINE_DELAY[delays$AIRLINE == "AA"],
     main = "Histogram of American Airlines Delays",
     xlab = "Flight Delay in Minutes")
```

```{r chunk3, error = T}
# Run this code chunk to create a histogram for the flight delays for Delta Airlines
hist(delays$AIRLINE_DELAY[delays$AIRLINE == "DL"],
     main = "Histogram of Delta Airlines Delays",
     xlab = "Flight Delay in Minutes")
```

Check the conditions below:

**Replace this text with your check of the conditions**

## Question 3:
Conduct the test of the hypotheses you stated above.

```{r chunk4, error = T}
# Run this chunk to get the hypothesis test 
t.test(AIRLINE_DELAY ~ AIRLINE, data = delays, mu = 0, alternative = "REPLACE THIS TEXT TO MATCH YOUR ALTERNATIVE HYPOTHESIS--be sure to keep the quotation marks")
```

a. The value of the test statistic is **replace this text with the value of the test statistic**, and the *p*-value is **replace this text with the p-value**.

b. Do you reject or fail to reject the null hypothesis at the 0.10 significance level? Why?

**replace this text with your answer to part b**

c. Write a conclusion in context.

**replace this text with your answer to part c**

d. Would your decision to reject or fail to reject the null hypothesis be the same at the 0.05 significance level? Why or why not?

**replace this text with your answer to part d**

## Question 4:
Use R to calculate a 90% confidence interval for the difference in the average delay time in minutes (`AIRLINE_DELAY`) for American Airlines flights and Delta Airlines flights (`AIRLINE`) leaving Detroit Metro Airport.

```{r chunk5, error = T}
t.test(AIRLINE_DELAY ~ AIRLINE, data = delays, conf.level = 0.9)
```

Based on this 90% confidence interval, which airline would you recommend to your roommate, American Airlines, Delta Airlines, or no preference? Explain why. Be sure to include numerical evidence.

**replace this text with your answer to Question 4**


