---
title: "PSTAT 5LS Lab 4 Part 2 Notes"
author: "Your Name Here"
date: "Week of February 12"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats250sbi)
```

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Code

Use the chunks below to try out any code that you'd like. 

```{r setSeed, error = T}
# Run this code chunk to set the seed
set.seed(734)
```

```{r sim1, error = T}
# Run this code chunk to run the simulation for the pets hypothesis test 
sim1 <- simulate_chance_model(chanceSuccess = 0.67, 
                              numDraws = 480, 
                              numRepetitions = 500)
```

```{r histSimulate, error = T}
# Run this code chunk to create the histogram of sim1, including the two red vertical lines
hist(sim1, 
     main = "Histogram of 500 Simulation Results",
     xlab = "Simulated proportion of U.S households with at least one pet")
abline(v = 0.7, col = "red")
abline(v = 0.64, col = "red")
```

```{r pvalue_sim, error = T}
# Run this code chunk to find the two-sided p-value of the simulation
sum(sim1 >= 0.70 | sim1 <= 0.64) / 500
```

```{r normalDistCode, error = T}
# Run this code chunk to visualize the p-value using the N(0, 1) distribution
plot_norm(mean = 0.67, 
          sd = 0.021, 
          shadeValues = c(0.64, 0.7), 
          direction = "beyond", 
          col.shade = "darkgreen")
```

```{r computeSE, error = T}
# Run this code chunk to compute the standard error for the normal distribution
p_0 <- 0.67
n <- 480
SE <- sqrt(p_0*(1 - p_0)/n)
SE 
```

```{r prop_test_pet, error = T}
# Run this code chunk to use prop_test() to find the p-value based on the normal theory
prop_test(x = 336, 
          n = 480, 
          p = 0.67, 
          alternative = "two.sided")
```

```{r pvalue}
# Run this code chunk to use calculate the p-value using the normal theory
2 * pnorm(q = 0.7, 
      mean = 0.67, 
      sd = 0.021, 
      lower.tail = FALSE)
```

Each of the three previous approaches to finding the p-value will produce a slightly different result. **No need to worry about how close the values should be, or which value is "best".**

```{r prop_test_pet2, echo = FALSE}
# Run this code and examine the 95% confidence interval 
prop_test(x = 336, 
          n = 480, 
          p = 0.67, 
          alternative = "two.sided")
```

```{r prop_test_pet3, echo = FALSE}
# Run this code to get a 98% confidence interval 
prop_test(x = 336, 
          n = 480, 
          p = 0.67, 
          alternative = "two.sided", 
          conf.level = 0.98)
```

# Code Cheat Sheet

## `set.seed(seed)`
Sets the "seed" of R's random number generator. After setting the seed, the sequence of random numbers R will produce is entirely determined/predictable. This is useful for ensuring you get the same results whenever you knit your code.

- `seed` is an integer. The seed you want to set.

## `simulate_chance_model(chanceSuccess, numDraws, numRepetitions)`

- `chanceSuccess`: a number between 0 and 1 represending the probability of observing a "success"
- `numDraws`: the number of times to draw a poker chip from the bag needed to coplete one repetition of the simulation
- `numRepetitions`: the number of times to repeat the simulation process

## `abline(linear_model_name)`

- Will plot the line found in `linear_model_name`
- Use `v = value` to print a vertical line

## `plot_norm()` 

- `mean`: the mean of the normal distribution you'd like to draw ($\mu$)
- `sd`: the standard deviation or standard error of the normal distribution you'd like to draw ($\sigma$ or $\sqrt{\frac{p_0(1-p_0)}{n}}$, respectively)
- `shadeValues` (optional): either a number or a vector of two numbers (using `c()`) that are the boundaries of the region you'd like to shade.
- `direction`: where to shade (`"less"`, `"greater"`, `"between"`, or `"beyond"`)
- `col.shade`: the color to use when shading
- any other graphical parameters you want to use to control the appearance of the plot (like `main`, etc.)

## `prop_test(x, n, p, alternative)`

- `x`: the number of successes observed in the study
- `n`: the sample size of the study
- `p`: the value of the null hypothesis
- `alternative`: the direction of the alternative hypothesis; choices are `"two.sided"` (default), `"greater"`, or `"less"`

## `pnorm(q, mean, sd, lower.tail = TRUE)`

- `q`: the x-axis value you want to find an area related to
- `mean`: the mean of the normal distribution, defaults to 0
- `sd`: the standard deviation of the normal distribution, defaults to 1
- `lower.tail` determines whether `pnorm()` finds the area to the left or right of `q`. If `lower.tail` is set to \textcolor{blue}{`TRUE`} (the default), it shades to the \textcolor{blue}{LEFT} If `lower.tail` is set to \textcolor{red}{`FALSE`}, it shades to the \textcolor{red}{RIGHT}.

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes
