---
title: "PSTAT 5LS Lab 4 Report"
author: "YOUR NAME GOES HERE - KEEP THE QUOTES"
date: "TODAY'S DATE GOES HERE - KEEP THE QUOTES"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats250sbi)
```

# Introduction

Higher Ed Dive reported that 43% of students applying for college included their SAT and/or ACT score in the 2022-2023 application year.  

In a survey of high school students in a large metropolitan area, 74 out of 200 students surveyed reported including their SAT and/or ACT score in the 2022-2023 application year. **Is there evidence to suggest that the proportion of high school students in this large metropolitan area who included their SAT and/or ACT score in their college application is different from the national rate of 43%?** 

## Hypotheses
Write the null and alternative hypotheses below.
Please fill in your answer where it says **"Write your answer here"**.

$H_0$: **Write your answer here in symbols**

$H_A$: **Write your answer here in symbols**

where **write your symbol here** represents **write your answer here**.

## Calculations
Assume the conditions for inference are satisfied. Use `prop_test()` to find the test statistic and p-value.

```{r codeBlock1, error = T}
# Use this code chunk to run the hypothesis test. 


```

Please fill in your answer where it says **"Write your answer here"**.

The test statistic is **"Write your answer here"**.
The p-value is **"Write your answer here"**.

## Decision and Conclusion
Please fill in your answer where it says **"Write your answer here"**.

Do you reject or fail to reject the null hypothesis at the 10% significance level? Why?
**"Write your answer here"**

Does your analysis suggest that the proportion of high school students in this large metropolitan area who included their SAT and/or ACT score in their college application is different from the national rate of 43%? 
**"Write your answer here"**

## Confidence Interval
Calculate a 90% confidence interval for the proportion of high school students in this large metropolitan area who included their SAT and/or ACT score in their college application. 

```{r codeBlock2, error = T}
# Use this code chunk to calculate the 90% confidence interval. 


```

We estimate with 90% confidence that the proportion of high school students in this large metropolitan area who included their SAT and/or ACT score in their college application is between **"Write your answer here"**.

